### 2022-10-03 chapters/optimization/java-dir/java.tex
add : example

\section{Tools and contributions}
\textsf{J-Referral} is an open-source tool designed to assist developers and practitioners in selecting the most energy-efficient JVM configuration for their software..
\Cref{table:j-referral} illustrates an example of the final report returned by \textsf{J-Referral}.
The tool was tested for 2 Java projects: \textsf{Zip4J}\footnote{\url{https://github.com/srikanth-lingala/zip4j}} and \textsf{K-nucleotide}.\footnote{\url{https://benchmarksgame-team.pages.debian.net/benchmarksgame/performance/knucleotide.html}}
\textsf{Zip4J} runs a large file compression, while \textsf{K-nucleotide} extracts a DNA sequence, and updates a hashtable of k-nucleotide keys to count specific values.
The short report presented in \Cref{table:j-referral} shows the ratio of potential energy saving between the most and least energy consuming tested JVM (40\% and 70\% energy savings for \textsf{Zip4J} and \textsf{K-nucleotide}, respectively).
Options are available for \textsf{J-Referral} to obtain much more detailed reports including execution time, DRAM usage, split DRAM vs. CPU consumption, etc.
The tool is available as \emph{open-source software} (OSS) from our GitHub repository.\footnote{\url{https://github.com/chakib-belgaid/jreferral}}

>>>>

\section{Tools and contributions}
\textsf{J-Referral} is an open-source tool designed to assist developers and practitioners in selecting the most energy-efficient JVM configuration for their software.
\Cref{table:j-referral} illustrates an example of the final report returned by \textsf{J-Referral}.
The tool was tested for 2 Java projects: \textsf{Zip4J}\footnote{\url{https://github.com/srikanth-lingala/zip4j}} and \textsf{K-nucleotide}.\footnote{\url{https://benchmarksgame-team.pages.debian.net/benchmarksgame/performance/knucleotide.html}}
\textsf{Zip4J} runs a large file compression, while \textsf{K-nucleotide} extracts a DNA sequence, and updates a hashtable of k-nucleotide keys to count specific values.
The short report presented in \Cref{table:j-referral} shows the ratio of potential energy saving between the most and least energy consuming tested JVM (40\% and 70\% energy savings for \textsf{Zip4J} and \textsf{K-nucleotide}, respectively).
Options are available for \textsf{J-Referral} to obtain much more detailed reports including execution time, DRAM usage, split DRAM vs. CPU consumption, etc.
The tool is available as \emph{open-source software} (OSS) from our GitHub repository.\footnote{\url{https://github.com/chakib-belgaid/jreferral}}
